Categorical Predictor Embeddings in Actuarial Modeling

### 2021-03-16 manuscript/manuscript.Rmd
start adding viz

@@

## Interpretations {#interpretation}

- model explainability is important in insurance
- the more we can learn about how we arrive at our models the better
- cite some existing work on explainable models in actuarial literature to show people care
- refer back to some definitions from previous sections
- show some embedding weights from our models - 1d line plot
- (need a multidimensional embedding for this) do some pca/tsne
- stress that relationship of embedding weights to response variable may be nonlinear depending on architecture

>>>>

## Visualization Techniques for Interpretation {#interpretation}

With AI and ML coming into the mainstream across industries and use cases, the topic of model explainability
has received increasing attention. In insurance pricing, @kuo2020explainability propose a framework for
model interpretability in the context of regulation and actuarial standards of practice, while @henckaerts2020boosting
investigate algorithm-specific techniques to inspect tree-based models. @kuo2020explainability and references
therein also discuss
commonly utilized model-agnostic explanation techniques, such as permutation variable importance and partial
dependence plots, that can be applied to the neural networks we consider in this paper.

In this section, we focus on ways to visualize the learned embeddings. In the authors' experiences, oftentimes
the formats of the visualizations --- basic line and scatter plots --- even more so than the content of the data, is 
helpful in explaining the concept to stakeholders.

For Model 2, the neural network with one-dimensional embeddings, the task is simple: we can simply plot the levels
on a line, as in Figure \@ref(fig:num-floors). In the case of `flood_zone`, since we happen to have the luxury of knowing a
priori the meaning of the prefixes, we can plot them separately to see how the model mapped them. (TODO insert chart).
(insert any observations).

```{r num-floors, echo=FALSE, fig.cap="Number of floors", out.width = "90%", fig.align="center"}
knitr::include_graphics("images/num_floors.png")
```

For Model 4, the neural network with multi-dimensional embeddings, we would need to treat the learned values before
we can plot them. Specifically, we need to reduce the dimension of the data to 2D for embeddings with more than
two dimensions. The standard approachs for this are principal component analysis (PCA) and t-distributed stochastic
neighbor embedding (t-SNE), both of which we illustrate below.

### PCA

### t-SNE

@@
